### 2018-10-04 README.Rmd
formatting to submit

@@

> Cascalheira, J., Horta, P., Bicho, N. (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for 'The role of lithic bipolar technology in Western Iberia’s Upper Paleolithic: the case of Vale Boi (southern Portugal)'_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

There are no actual R functions in this package - all the R code is in the Rmd file. I simply used the R package structure to help manage dependencies, to take advantage of continuous integration for automated code testing, and so I didn't have to think too much about how to organise the files.

@@

Once the download is complete, open the ShortTermOccupations.Rproj in RStudio to begin working with the package and compendium files.

The package has a number of dependencies on other R packages, and programs outside of R. Installing these can be time-consuming and complicated, so we've included a packrat directory, which contains the source code for all the packages we depend on. If all works well, these will be installed on your computer when you open ShortTermOccupations.Rproj in RStudio.

>>>>

[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-brightgreen.svg)](https://github.com/jmcascalheira/ScaledPiecesVB/commits/master)
[![minimal R version](https://img.shields.io/badge/R%3E%3D-3.2.4-brightgreen.svg)](https://cran.r-project.org/) 
[![Build Status](https://travis-ci.org/jmcascalheira/ScaledPiecesVB.svg?branch=master)](https://travis-ci.org/jmcascalheira/ScaledPiecesVB)
[![Licence](https://img.shields.io/github/license/mashape/apistatus.svg)](http://choosealicense.com/licenses/mit/)
[![ORCiD](https://img.shields.io/badge/ORCiD-/0000--0003--0321--8892-green.svg)](http://orcid.org/0000-0003-0321-8892)

@@

> Cascalheira, J., Horta, P., Bicho, N. (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for 'The role of lithic bipolar technology in Western Iberia’s Upper Paleolithic: the case of Vale Boi (southern Portugal)'_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.17605/OSF.IO/WPXGH>

@@

@@

Once the download is complete, open the ScaledPieces.Rproj in RStudio to begin working with the package and compendium files.

The package has a number of dependencies on other R packages, and programs outside of R. Installing these can be time-consuming and complicated, so we've included a packrat directory, which contains the source code for all the packages we depend on. If all works well, these will be installed on your computer when you open ScaledPiecesVB.Rproj in RStudio.
